---
title: "Into to R"
output: html_document
date: "2023-04-17"
---

```{r setup, include=FALSE, echo=F}
# Above is how a r chunk is set up
# To set up a r chunk you use three ``` followed by a {} with r as the first input
# After ```{r} you can have the chunk named. In this case this chunk is named setup
# Following the naming of the chunk you can have chunk settings. There are many many settings available and you will learn them with time. 
# This chunk has include set to FALSE and echo set to TRUE. Notice that you can use the word FALSE in all capital letter or F capitalized in place of FALSE. This is up to your personal preference and the same can be done for TRUE (T). 
#The chunk must be ended with another three ``` before creating the next chunk

#_____________________________________________#

# When you first want to use a package you will need to install it
# This is done using the function install.packages()
# After installing a package it will be on your computer until you remove it
# You will occasionally need to update your packages but that is not a regular thing
# install.packages("tidyverse","ggplot2","readxl")

# After a package is installed you will need to activate it
# This is done with the function library()
# For each package you will need a separate library call to activate it
library(tidyverse)
library(ggplot2)

# If you do not want a line of code to run you can comment it as seen here.
# A comment is made anytime you use a # and will result in the text commented being skipped when the code is run. 

#library(readxl)

#____IMPORTANT____#
# If you are ever confused about a function use the ? in the below command console to view its help file.
# This would look like ?mutate
# The help tab on the right side of the screen will display helpful information about that function
#_________________#


```

```{r data setup, echo= F}
# For this tutorial we will be using the mtcars dataset which come with R.
# The function view() will allows you to visualize a dataframe in R (more on that later). 
# Note: A new tab will be opened at the top of this window. 
view(mtcars)

# You can see that the mtcars dataset has 11 columns, 32 rows, and a special column (the left most column) called rownames. 

# We can not work with the mtcars dataset in this state so we need to load it into our environment (upper right corner tab) under a name of our choice. We will name this dataframe r_intro_cars using the <- operation which looks like an arrow. 

r_into_cars <- mtcars

# Opps, I seems to have made a mistake when naming our dataframe. I accidentally forgot misspelled intro as into.
# We can fix this using the function rm() which removes an object from our environment

rm(r_into_cars)

# Now the mtcars dataset is gone from our global environment and we will fix the name as r_intro_cars. 
# This can be done by fixing the name on line 53 of this code. However, I want to keep this tutorial linear so I will rewrite the code with the new fixed name below. 

r_intro_cars <- mtcars

# It is important to not have any spaces when naming objects in R. Spaces do not work well and will cause headaches down the road. Get used to using underscores _ in the place of spaces. 

# Now we have loaded the mtcars dataset into our global environment as a dataframe. In the next chunk we will manipulate this dataframe using pipes. 

```

```{r data manipulation, echo=F}

# There are countless ways to manipulate data but pipes will be used throughout them all. They allow ease of coding by providing a logical path from one function to another with the output of all pipes being saved as an R object in the global environment. 

four_cyl_liters_per_100k <- r_intro_cars %>% filter(cyl == 4) %>% mutate(L_per_100k = 235.215/mpg, .before = "mpg")

# The above code takes our r_intro_cars dataframe and filters it so only cars with 4 cylinder engines are left. Then we mutate the miles per gallon (mpg) column to liters per 100 kilometres by dividing 235.215 by the value in the mpg column. Finally a new column is made called L_per_100k before the column mpg with the value we calculated. 

# Now view the new dataframe object to see how it changed. You can use view(four_cyl_liters_per_100k) or you can click on the dataframe object in the environment tab to the upper right. 

# Now say you want to filter so you only have cars with a 4 cylinder engine and their horsepower is greater than 90. The code for that would be as follows. 

four_cyl_hp_90 <- r_intro_cars %>% filter(cyl == 4 & hp > 90) %>% mutate(L_per_100k = 235.215/mpg)

# Within a filter you can use & for AND, | for OR, and ! for negate. 

no_four_cyl_hp_90 <- r_intro_cars %>% filter(!cyl == 4 & hp > 120) %>% mutate(L_per_100k = 235.215/mpg)

# Here we omit all 4 cylinder engines and only select those from the remaining which have a horsepower over 120

# You can learn more ways to use these by using ? on filter and mutate


```

```{r data manipulation continued}

# You can clean up your R code be using script to run specific chunks of code. 

# The source() function allows you to run code in .R file types before the rest of the code in the chunk is run.

# To make a script, go to "file" on the top bar of R studio. Then select "new file" and the first option will be "script". 

source("demo_folder/cassie_source.R")

# Joining one dataframe to another is a very useful technique to linking data. 

# First you need two dataframes to join together. We will be joining source cars with a dataframe I made up (below).

made_up_dat <- data.frame(rowname = source_cars[,1],mpg = source_cars[,2],vroominess = "vroom")

# This joins one dataframe to another based on a common column (or a key ID column)

vroom_dat <- source_cars_named %>% left_join(made_up_dat, by = "rowname")

# You can also join based on multiple columns

vroom_dat <- source_cars_named %>% left_join(made_up_dat, by = c("rowname", "mpg"))


```


```{r more advance data manipulation, echo=F, include=F}
# Here we will take a dataset, manipulate it, and display it on a map.

# First clear the environment by clicking the broom icon in the environment tab.

# Then we will load in and manipulate the csv dataset.
# read_csv() from the readxl package is great for reading in csv files. 
dat_beetles <- read_csv("PST_IF_PTC.csv", col_names = T) %>% 
  # Here we rename the columns using the rename() function to something more intuitive.
  rename("Common_name" = "PST_CMN_NM",
         "Latin_name" = "PST_LTN_NM",
         "Species_code" = "PST_SPC_CD",
         "Year" = "CPTR_YR",
         "lat" = "X",
         "long" = "Y",
         "unit_number" = "ORG_UNITNO",
         "Tree_code" = "TR_SPCS_CD",
         "Tree_name" = "TR_CM_NM",
         "Area_ha" = "AREA_HA") %>%
  # Here we get rid of all other columns from the original dataset we do not need.
  select(c(lat,long,"Common_name", "Latin_name","Year","unit_number","Species_code")) %>% 
  # This is more advance, but here we create a new column called species_code and make a specific code be used for each beetle name in the Common_name column. The last TRUE part makes any names I missed be kept in the new column. 
  mutate(species_code = case_when(Common_name == "Western Balsam Bark Beetle" ~ "IBB",
                                  Common_name == "Spruce Beetle" ~ "ISB",
                                  Common_name == "Douglas-fir Beetle" ~ "IBD",
                                  Common_name == "Flooding" ~ NA,
                                  Common_name == "Post-burn Mortality" ~ NA,
                                  Common_name == "Mountain Pine Beetle" ~ "IBM",
                                  Common_name == "Slide" ~ NA,
                                  TRUE ~ Common_name)) %>% 
  # Finally we filter the names as we need. 
  filter(Common_name %in% c("Western Balsam Bark Beetle","Spruce Beetle","Douglas-fir Beetle","Mountain Pine Beetle","Bark Beetles","Western Pine Beetle"))

#install.packages("elevatr","sf")

library(elevatr)
library(sf)

# We will now use the elevatr package to add elevation information to our dataframe based on lat and long location. 

# First we must project our dataframe to a coordinate system using the sf package. 

dat_beetles_projected <- dat_beetles %>%
  # convert the data frame into a simple feature.
  st_as_sf(
    # set the column names with your point coordinates.
    coords = c('lat', 'long'),
    # set your coordinate reference system, 4326 is lat/long.
    # the crs can be obtained from https://epsg.io/ if you do not know it.
    crs = 4326)


# Here we add elevation data to the beetle map based on the latitude and longitude of our spatial dataframe.
# By making z larger (more detail) or smaller (less detail) you can impact how fast the process takes. 
# This dataset is large and takes a while so load the rda file instead
#dat_beetles_elevation <- get_elev_point(dat_beetles_projected, prj = 4326, src = "aws", z = 10)

#Increasing z in the above code makes you have a finer evolution resolution 
# By saving a dataframe (or any R object) as a .rda file you can load in the results of analysis that take a long time to run therefore saving you time in the future. 
#save(dat_beetles_elevation, file = "dat_beetles_elevation.rda")

load(file = "dat_beetles_elevation.rda")


```



```{r Beetle interactive map}

#install.packages("leaflet","leaflet.extras","htmltools","htmlwidgets","leafem")

library(leaflet)
library(leaflet.extras)
library(htmltools)
library(htmlwidgets)
library(leafem)

# Create a palate of colours for map based off of common names of beetles
pal.beetle_name <- colorFactor(palette = "Set1", domain = dat_beetles_elevation$Common_name, reverse = T)

# unique(dat_beetles_elevation$Common_name)

# Needed to make a custom colour palate for factors greater than 11
c25 <- c(
  "dodgerblue2", "#E31A1C", 
  "green4",
  "#6A3D9A",
  "#FF7F00",
  "black", "gold1",
  "skyblue2", "#FB9A99",
  "palegreen2",
  "#CAB2D6",
  "#FDBF6F", 
  "gray70", "khaki2",
  "maroon", "orchid1", "deeppink1", "blue1", "steelblue4",
  "darkturquoise", "green1", "yellow4", "yellow3",
  "darkorange4", "brown"
)

# Applying the custom colour palate to the unit number factors
pal.beetle_unit <- colorFactor(palette = c25, domain = dat_beetles_elevation$unit_number, reverse = T)

# Construct the interactive map for beetles across BC

interactive_beetle_map <- leaflet(dat_beetles_elevation) %>% 
  # These 4 lines of code add the base maps and mouse coordinates to the map.
  # Each group will be clickable on the map to be swapped between (except mouse). 
        addTiles(group = "OSM") %>% 
        addProviderTiles("CartoDB", group = "Carto") %>% 
        addProviderTiles("Esri", group = "Esri") %>%
        addMouseCoordinates() %>%
  # This part adds the circle markers to the map with popup bubbles for additional data. 
        addCircleMarkers(data = dat_beetles_elevation, radius = 2, 
                         group = dat_beetles_elevation$Common_name, color = ~pal.beetle_name(Common_name),
                         popup = ~paste("Common name: ","<b>", Common_name, "</b>", "<br/>",
                                         "Latin name:","<i>",Latin_name,"</i>", "<br/>",
                                         "Species code:", species_code, "<br/>",
                                         "Elevation: ", elevation,"m <br/>",
                                         "Unit Number: ", unit_number, "<br/>"),
                         label = ~htmlEscape(Common_name)) %>%
        addCircleMarkers(data = dat_beetles_elevation, radius = 2, 
                         group = "Unit Number", color = ~pal.beetle_unit(unit_number),
                         popup = ~paste("Common name: ","<b>", Common_name, "</b>", "<br/>",
                                         "Latin name:","<i>",Latin_name,"</i>", "<br/>",
                                         "Species code:", species_code, "<br/>",
                                         "Elevation: ", elevation,"m <br/>",
                                         "Unit Number: ", unit_number, "<br/>"),
                         label = ~htmlEscape(Common_name)) %>%
  # This code adds the ability to toggle layers on and off while interacting with the map.
        addLayersControl(baseGroups = c("OSM", "Carto", "Esri"), 
                         overlayGroups = c(dat_beetles_elevation$Common_name, "Unit Number")) %>% 
  # This adds a legend to the map
        addLegend(position = "bottomright",
            pal = pal.beetle_name, values = ~Common_name, opacity = 1, title = "Beetle Common Names", group = dat_beetles_elevation$Common_name) %>%
        addLegend(position = "bottomleft",
            pal = pal.beetle_unit, values = ~unit_number, opacity = 1, title = "Unit Names",group = "Unit Number") %>%
  # A minimap helps the user identify where they are in respect to other geographical landmarks. 
        addMiniMap(position = "topleft") %>%
  # This determines where the user starts when viewing the map. 
        setView(lat = 53.876, lng = -122.769 , zoom = 10)

#saveWidget(interactive_beetle_map, file="interactive_beetle_map.html")


# Create a palate of colours for map based off of beetle elevations
pal.beetle_elev <- colorNumeric(palette = "Set1", domain = dat_beetles_elevation$elevation, reverse = T)

interactive_beetle_elevation_map <- leaflet(dat_beetles_elevation) %>% 
        addTiles(group = "OSM") %>% 
        addProviderTiles("CartoDB", group = "Carto") %>% 
        addProviderTiles("Esri", group = "Esri") %>%
        addMouseCoordinates() %>%
        addCircleMarkers(data = dat_beetles_elevation, radius = 2, 
                         group = dat_beetles_elevation$Common_name, color = ~pal.beetle_elev(elevation),
                         popup = ~paste("Common name: ","<b>", Common_name, "</b>", "<br/>",
                                         "Latin name:","<i>",Latin_name,"</i>", "<br/>",
                                         "Species code:", species_code, "<br/>",
                                         "Elevation: ", elevation,"m <br/>",
                                         "Unit Number: ", unit_number, "<br/>"),
                         label = ~htmlEscape(Common_name)) %>% 
        addLayersControl(baseGroups = c("OSM", "Carto", "Esri"), 
                         overlayGroups = c(dat_beetles_elevation$Common_name)) %>% 
        addLegend(position = "bottomright",
            pal = pal.beetle_elev, values = ~elevation, opacity = 1, title = "Elevation (meters)") %>%
        setView(lat = 53.876, lng = -122.769 , zoom = 10) 



```

interactive_beetle_map

interactive_beetle_elevation_map

```{r diversity indecies, include=F,echo=F}
# Here we make a new dataframe based on the counts of beetles. 
dat_beetle_counts <- dat_beetles_elevation %>% mutate(beetle_zones = case_when(elevation < 900 ~ 1,
                                                                               elevation < 1100 ~ 2,
                                                                               elevation < 1300 ~ 3,
                                                                               elevation < 1500 ~ 4,
                                                                               elevation < 1700 ~ 5,
                                                                               elevation < 1900 ~ 6,
                                                                               elevation < 2100 ~ 7)) %>%
  # We group the data based on unit numbers
  group_by(unit_number) %>% 
  # We then summarise the sum of the values together to make a table of total beetles found in each group. 
  summarise(total = sum(Species_code %in% c("IBB","ISB","IBD","IBM","IB","IBD", "IAB", "IBW")),
            total_balsam = sum(Species_code == "IBB"),
            prop_balsam = total_balsam / total,
            total_spruce = sum(Species_code == "ISB"),
            prop_spruce = total_spruce / total,
            total_doug = sum(Species_code == "IBD"),
            prop_doug = total_doug / total, 
            total_mountain = sum(Species_code == "IBM"),
            prop_mountain = total_mountain / total, 
            total_bark = sum(Species_code == "IB"),
            prop_bark = total_bark / total,
            total_western = sum(Species_code == "IBW"),
            prop_western = total_western / total,
            group = unique(unit_number)) %>%
  # Here I just select what I want from what I made. 
  select(c(total_spruce,total_doug,total_balsam,total_mountain,total_bark,total_western,group)) %>%
  # Always remember to ungroup() after grouping to avoid issues down the line. 
  ungroup()

# Here I just get rid of the geometry column (its annoying to get rid of otherwise).  
dat_beetle_counts$geometry <- NULL

# This is another way to join but by one column. I add the groups of the data to a specific dataframe with group names. I will need this down the line. 
dat_beetle_group_names <- dat_beetle_counts$group

dat_beetle_counts <- dat_beetle_counts %>% select(c(total_spruce,total_doug,total_balsam,total_mountain,total_bark,total_western))

# Makes the data into the form of a matrix
dat_beetle_counts <- as.matrix(dat_beetle_counts)

# Data needs to be in the form of a matrix
# q and alpha can be set to anything but i think 2 and 0.5 are standard. 
# Custom function using function() to make diversity formulas
alpha_diversity <- function(data, q, alpha) {
  p_ij <- data / rowSums(data)
  p_ij[is.na(p_ij)] <- 0
  p_i <- colSums(p_ij)
  p_i[p_i == 0] <- 1 # Handle cases where all species are absent
  p_i_given_j <- p_ij / matrix(p_i, nrow = nrow(p_ij), ncol = ncol(p_ij), byrow = TRUE)
  div <- 1 / ((rowSums(p_ij * p_i_given_j^(q - 1)))^(1 / (q - 1)))
  return(div^alpha)
}

# This gets us our alpha diversity based on our matrix of beetle totals per group.   
diversity_alpha <- alpha_diversity(dat_beetle_counts,2,0.5)

gamma_diversity <- function(data, q) {
  p_i <- colSums(data) / sum(data)
  sum_pq <- sum(p_i^q)
  1 / (sum_pq ^ (1/(q-1)))
}

# This gets us our gamma diversity based on our matrix of beetle totals per group.  
diversity_gamma <- gamma_diversity(dat_beetle_counts,2)

# This gets us our betal diversity based on our alpha and gamma diversities.
diversity_beta <- diversity_gamma/diversity_alpha

# Compute species richness
species_richness <- apply(dat_beetle_counts, 1, function(x) sum(x > 0))

# Compute Simpson's index
simpsons_index <- apply(dat_beetle_counts, 1, function(x) {
  p <- x[x > 0] / sum(x)
  1 - sum(p^2)
})

# Compute Shannon's index
shannons_index <- apply(dat_beetle_counts, 1, function(x) {
  p <- x[x > 0] / sum(x)
  -sum(p * log2(p))
})

# Here we cbind() (column bind) our group names dataframe to our new data. Allows for a more informative dataframe in the end. 
indexes <- as.data.frame(cbind(group_names = dat_beetle_group_names,species_richness,simpsons_index,shannons_index,diversity_alpha,diversity_beta))



```


```{r beetle linear modeling, warning=F}

#install.packages("broom","emmeans", "MuMIn")

library(broom)
library(emmeans)
library(MuMIn)

mod_beetles <- read_csv("PST_IF_PTC.csv", col_names = T) %>% 
  # Here we rename the columns using the rename() function to something more intuitive.
  rename("Common_name" = "PST_CMN_NM",
         "Latin_name" = "PST_LTN_NM",
         "Species_code" = "PST_SPC_CD",
         "Year" = "CPTR_YR",
         "lat" = "X",
         "long" = "Y",
         "unit_number" = "ORG_UNITNO",
         "Tree_code" = "TR_SPCS_CD",
         "Tree_name" = "TR_CM_NM",
         "Area_ha" = "AREA_HA") %>%
  select(c("Common_name","Latin_name","Species_code","Year","lat","long","unit_number","Tree_code","Tree_name","Area_ha")) %>% na.omit() %>% mutate(across(where(is.character) | unit_number, as.factor)) %>%
  filter(Common_name %in% c("Western Balsam Bark Beetle","Spruce Beetle","Douglas-fir Beetle","Mountain Pine Beetle","Bark Beetles","Balsam Woolly Adelgid","Western Pine Beetle"))

# mod_beetles_elevation <- mod_beetles %>%
#   st_as_sf(coords = c('lat', 'long'), crs = 4326) %>% get_elev_point(., prj = 4326, src = "aws", z = 10)

# mod_beetles_elevation$geometry <- NULL

# save(mod_beetles_elevation, file = "mod_beetles_elevation.rda")

load("mod_beetles_elevation.rda")

# Here we make a global (all variable) linear model using the lm() function. 
mod_linear <- lm(elevation ~ unit_number + Tree_code + Species_code + Area_ha, 
                 data = mod_beetles_elevation, na.action = na.fail)

#Takes a global model and runs smaller models with fixed effects removed to find best model
mod_linear_compare <- dredge(mod_linear)

# The best model does not include Area_ha as a fixed-effect

mod_linear_new <- lm(elevation ~ unit_number + Tree_code + Species_code, 
                 data = mod_beetles_elevation, na.action = na.fail)

# The summary() function gives you a bunch of useful information about models you run
summary(mod_linear_new)

# The tidy() function allows you to extract useful information from a model and display in a dataframe format.
mod_table <- tidy(mod_linear_new)

# Here we extract the fitted (predicted) values from the model as well as the residuals using the fitted() and resid() functions. We then put them into a dataframe for graphical display. 
fit_res <- data.frame(Fitted = fitted(mod_linear_new),
                      Residuals = resid(mod_linear_new))

# The following will utilize the ggplot2 package. These ways of testing linear model ONLY work with certain types (such as they will NOT work with binomial linear models). However, in this case we are using a default Gaussian distribution model.  

# Here we make a plot of the residual values. We want them to be fairly randomly dispersed around 0 with no clear pattern. If there is a pattern such as a wave or slope, then a linear model may not be an appropriate approach to the data and a non-linear approach would need to be explored. 
resid_plot <- ggplot(fit_res, aes(Fitted,Residuals)) + # set the aesthetics for the x and y axes
  geom_point() + 
  geom_hline(yintercept = 0,linetype = "dashed") + 
  xlab("Fitted") + 
  ylab("Residuals")+ 
  theme_bw()

# The quartile plot is another way of testing if your linear model is appropriate. You want your values to be along the line in the graph (made with stat_qq_line()). Some diversion on either end is ok as that just means there is some error (outliers) as you get further away. However you do not want to see anything far from the line. 
quartile_plot <- ggplot(fit_res, aes(sample = Residuals)) + # enter the variable for the aesthetics sample
  stat_qq()+
  stat_qq_line() +
  xlab("Residual quantiles") + 
  ylab("Theoretical quantiles") +
  theme_bw()

# This is the most straightforward plot. Do your residuals show you a normal distribution. In this case it does, however, some cases it may not (especially difficult with small datasets). 
resid_distribution_plot <- ggplot(fit_res, aes(Residuals)) + # set the aesthetics for the x axis
  geom_histogram(binwidth = 5,color="black",fill="white") + 
  xlab("Residuals") + 
  ylab("Frequency") + 
  theme_bw()

# This is not necessary for a linear model but may help explain some relationships. The emmip() function from the emeans package allows you to plot predicted outcomes based on certain fixed effects. 
# Here we see the elevation estimates and error of beetle species for each tree type and how that changes between different tree types. 
# Pay attention to when we used mixed-effect modeling on the same dataset and see how the error changes. 
emmip(mod_linear_new, ~ Tree_code|Species_code,data = mod_beetles_elevation, xlab = "Tree type", 
      level = 0.95, CI = T,
      ylab = "Predicted elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=0.5), legend.position = "bottom") +
  ggtitle("Linear model of elevation, beetle type and tree type") 


beetle_pred <- mod_beetles_elevation %>% mutate(predicted = predict(mod_linear_new))

```

resid_plot

quartile_plot

resid_distribution_plot

```{r mixed effect modeling, warning=F}

#install.packages("broom.mixed","lme4")

library(lme4)
library(broom.mixed)


# Here is our mixed effect model of beetle elevation. We have unit_number as a random effect with a random intercept (1|unit_number) and a slope of 1. I changed the control from "nloptwrap" which is the default to "bobyqa" to speed up the analysis and help convergence. 
mod_mixed <- lmer(elevation ~ Tree_code + Species_code + Area_ha + (1|unit_number), 
                 data = mod_beetles_elevation,
                       control = lmerControl(optimizer = "bobyqa"), na.action = na.fail)

summary(mod_mixed)

mod_mixed_table <- tidy(mod_mixed)

#Takes a global model and runs smaller models with fixed effects removed to find best model
mod_mixed_compare <- dredge(mod_mixed)

# Best model (lowest AIC and highest weight) is one with all variables
# There is the possibility that no one model is the best model. If the model weights are less than 90% then you may have to utilize model averaging (not shown in this tutorial) to create a model that best explains the data. 
view(mod_mixed_compare)

fit_res_mixed <- data.frame(Fitted = fitted(mod_mixed),
                      Residuals = resid(mod_mixed))

resid_plot_mixed <- ggplot(fit_res_mixed, aes(Fitted,Residuals)) + # set the aesthetics for the x and y axes
  geom_point() + 
  geom_hline(yintercept = 0,linetype = "dashed") + 
  xlab("Fitted") + 
  ylab("Residuals")+ 
  theme_bw()

quartile_plot_mixed <- ggplot(fit_res_mixed, aes(sample = Residuals)) + # enter the variable for the aesthetics sample
  stat_qq()+
  stat_qq_line() +
  xlab("Residual quantiles") + 
  ylab("Theoretical quantiles") +
  theme_bw()

resid_distribution_plot_mixed <- ggplot(fit_res_mixed, aes(Residuals)) + # set the aesthetics for the x axis
  geom_histogram(binwidth = 5,color="black",fill="white") + 
  xlab("Residuals") + 
  ylab("Frequency") + 
  theme_bw()


emmip(mod_mixed, ~ Tree_code|Species_code,data = mod_beetles_elevation, xlab = "Tree type", 
      level = 0.95, CI = T,
      ylab = "Predicted elevation (m)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0, hjust=0.5), legend.position = "bottom") +
  ggtitle("Mixed model of elevation, beetle type and tree type") 

# Write data to a csv

# write_csv(mod_linear_compare, file = "linear_model.xlsx")


```

resid_plot_mixed
quartile_plot_mixed
resid_distribution_plot_mixed

